\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt] \huge Project Title \\

### 2020-05-30 manuscript/manuscript.tex
updated pipeline

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{Figures/test.png}
  \caption{Notice how \LaTeX\ automatically numbers this figure.}
\end{figure}

>>>>

% drawing neural network
\usepackage{tikz}
\usetikzlibrary{shapes, arrows}
\tikzset{
  every neuron/.style={
    circle,
    draw,
    minimum size=0.5cm
  },
  neuron missing/.style={
    draw=none, 
    scale=3,
    text height=0.333cm,
    execute at begin node=\color{black}$\vdots$
  },
}

\usepackage{ifthen}
\newcommand{\foo}[1]{%
  \ifthenelse{\equal{#1}{missing}}
    {}
    {$H_{\l}$}
}

\newcommand{\lmao}[1]{%
  \ifthenelse{\equal{#1}{missing}}
    {}
    {$I_{\l}$}
}

% define flowchart styles
\tikzstyle{block} = [rectangle, rounded corners, minimum height=4em, draw=black, inner sep=1em]
\tikzstyle[line] = [draw, -latex']
\tikzstyle{stop} = [rectangle, rounded corners, minimum width=2cm, minimum height=0.5cm,text centered, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\begin{figure}[!ht]
    \centering
    \begin{tikzpicture}[node distance=6em, auto]
        % blocks
        \node [block, text width=16em] (init) {Collect data from GDSC (1,110 cell lines, 251 drugs).};
        \node [block, below of=init, text width=16em, yshift=-1em] (process) {Filter data: retain drugs with $>$80\% data for cell lines (548 cell lines, 117 drugs). Matrix normalization on IC50 via z-score.};
        \node [block, below of=process, text width=16em, yshift=-1.25em] (kmeans) {K-means clustering into 2 response groups (verified via elbow graph).};
        \node [block, below of=kmeans, text width=16em, yshift=-0.5em] (append) {Appended GDSC Affymetrix Human Genome U219 expression data to the IC50 matrix.};
        \node [block, below of=append, text width=16em, yshift=-1em] (feat) {Feature selection for relevant genes in RNA-seq data via Boruta algorithm. 300 genes selected at $\alpha=0.05$.};
        \node [block, below of=feat, text width=16em, yshift=-2.25em] (neural) {Hyperparameter optimization of neural network with varying number of hidden layers via grid search. Models evaluated via 5-fold cross-validation.};
        \node [block, below of=neural, text width=16em, yshift=-1.5em] (annot) {Functional annotation of predictive genes.};

        % arrows
        \draw [arrow] (init) -- (process);
        \draw [arrow] (process) -- (kmeans);
        \draw [arrow] (kmeans) -- (append);
        \draw [arrow] (append) -- (feat);
        \draw [arrow] (feat) -- (neural);
        \draw [arrow] (neural) -- (annot);
    \end{tikzpicture}
    \label{fig:flowchart}
    \caption{Summary of the data analysis pipeline.}
\end{figure}

\begin{figure*}[!ht]
    \centering
    \begin{tikzpicture}[x=1.5cm, y=1.5cm, >=stealth]

        % nodes
        \foreach \m/\l [count=\y] in {1,missing,n}
            \node [every neuron/.try, neuron \m/.try] (input-\m) at (0,-1.5-\y) {\lmao{\l}};

        \foreach \m/\l [count=\y] in {1,2,missing,2n}
            \node [every neuron/.try, neuron \m/.try] (hidden-\m) at (1.5,-1-\y) {\foo{\l}};

        \foreach \m/\l [count=\y] in {1,2,3,4,missing,4n}
            \node [every neuron/.try, neuron \m/.try] (hidden1-\m) at (3,0-\y) {\foo{\l}};

        \foreach \m/\l [count=\y] in {1,2,3,4,missing,4n}
            \node [every neuron/.try, neuron \m/.try] (hidden2-\m) at (4.5,0-\y) {\foo{\l}};

        \foreach \m/\l [count=\y] in {1,2,missing,2n}
            \node [every neuron/.try, neuron \m/.try] (hidden3-\m) at (6,-1-\y) {\foo{\l}};

        \foreach \m/\l [count=\y] in {1}
            \node [every neuron/.try, neuron \m/.try] (output-\m) at (7.5,0-2.5-\y) {$O_1$};

        % arrows
        \foreach \l [count=\i] in {1,n}
            \draw [<-] (input-\l) -- ++(-1,0) node [above, midway] {};

        \foreach \l [count=\i] in {1,n}
            \foreach \k [count=\j] in {1,2,2n}
              \draw [->] (input-\l) -- (hidden-\k);

        \foreach \l [count=\i] in {1,2,2n}
            \foreach \k [count=\j] in {1,...,4,4n}
              \draw [->] (hidden-\l) -- (hidden1-\k);

        \foreach \l [count=\i] in {1,...,4,4n}
            \foreach \k [count=\j] in {1,...,4,4n}
              \draw [->] (hidden1-\l) -- (hidden2-\k);

        \foreach \l [count=\i] in {1,...,4,4n}
            \foreach \k [count=\j] in {1,2,2n}
              \draw [->] (hidden2-\l) -- (hidden3-\k);

        \foreach \l [count=\i] in {1,2,2n}
            \foreach \k [count=\j] in {1}
              \draw [->] (hidden3-\l) -- (output-\k);

        % labelling layers
        \foreach \l [count=\x from 0] in {Input\\layer, Hidden\\layer 1, Hidden\\layer 2, Hidden\\layer 3, Hidden\\layer 4, Output\\layer}
            \node [align=left, above] at (\x*1.5, -0.5) {\l};

    \end{tikzpicture}
    \label{fig:neural_vis}
    \caption{Neural network architecture representation with four hidden layers ($n=300$). Inputs include the feature-selected genes from the RNA-seq dataset. Each hidden layer has a dropout rate of 0.3 and is subject to batch normalization.}
\end{figure*}

@@
